Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-13 manuscript/manuscript.tex
Fixed typos

The tesseroid size ratio included in the inequation 
\ref{eq:delta-density} is intended to reduce the number of probable 
unneeded discretizations and focus on discretizations that will 
significantly reduce the numerical error.
A big subdiving tesseroid with small maximum absolute difference would 
introduce more numerical error than a small subdividing tesseroid with 
higher maximum absolute difference.

@@

On Figure \ref{fig:density-discretization-algorithm}(a) we propose an 
arbitrary normalised density function as an example of how this 
algorithm works.
And we plotted its corresponding linear function $\rho_l(r')$ and a 
dashed line that represents the maximum absolute difference $\Delta 
\rho (r')$.
We will assume that the discretization inequation 
\ref{eq:delta-density} holds in this case, so we must divide the 
tesseroid at the height at which the maximum difference occurs.
The dots on Figure \ref{fig:density-discretization-algorithm} 
represent the discretization heights, i.e. the radial boundaries of the 
subdiving tesseroids produced by the algorithm.

@@

On Figure \ref{fig:density-discretization-algorithm}(c) we perform the 
same analysis on the deeper subdiving tesseroid, and assuming that the 
inequality holds in this case we also subdivide it.

Finally, if we suppose that the value of $\delta$ used in this example 
does not produce further discretizations, the resulting subdiving 
tesseroids can be seen on Figure 
\ref{fig:density-discretization-algorithm}(d).

@@

Lets consider a spherical shell with inner and outer radii $R_1$ and 
$R_2$, respectivetly, whose density depends on the radial spherical 
coordinate (Figure \ref{fig:spherical-shell}).
The gravity potential generated by the shell on an arbitrary external 
point $Q(0,0,r)$, located along the $z$ axe at a distance $r$ from the 
origin, can be written as follows:

@@

This expression will allow us  to perform comparisons between the 
anaytical solutions and the numerical approximation, similar as the 
ones made for the linear density case.
Although in the exponential density scenario the problem is more 
complex due to the fact that the density-based discretization must be 
used together with the modified adaptive discretization algorithm.
This means that both the distance-size ratio $D$ and the delta ratio 
$\delta$ must be simultaneously determined.

>>>>

The tesseroid size ratio included in the inequation 
\ref{eq:delta-density} is intended to reduce the number of probable 
unneeded discretizations and focus on discretizations that will 
significantly reduce the numerical error.
A big subdividing tesseroid with small maximum absolute difference would 
introduce more numerical error than a small subdividing tesseroid with 
higher maximum absolute difference.

@@

On Figure \ref{fig:density-discretization-algorithm}(a) we propose an 
arbitrary normalised density function as an example of how this 
algorithm works.
And we plotted its corresponding linear function $\rho_l(r')$ and a 
dashed line that represents the maximum absolute difference $\Delta 
\rho (r')$.
We will assume that the discretization inequation 
\ref{eq:delta-density} holds in this case, so we must divide the 
tesseroid at the height at which the maximum difference occurs.
The dots on Figure \ref{fig:density-discretization-algorithm} 
represent the discretization heights, i.e. the radial boundaries of the 
subdividing tesseroids produced by the algorithm.

@@

On Figure \ref{fig:density-discretization-algorithm}(c) we perform the 
same analysis on the deeper subdividing tesseroid, and assuming that the 
inequality holds in this case we also subdivide it.

Finally, if we suppose that the value of $\delta$ used in this example 
does not produce further discretizations, the resulting subdividing 
tesseroids can be seen on Figure 
\ref{fig:density-discretization-algorithm}(d).

@@

Lets consider a spherical shell with inner and outer radii $R_1$ and 
$R_2$, respectively, whose density depends on the radial spherical 
coordinate (Figure \ref{fig:spherical-shell}).
The gravity potential generated by the shell on an arbitrary external 
point $Q(0,0,r)$, located along the $z$ axe at a distance $r$ from the 
origin, can be written as follows:

@@

This expression will allow us  to perform comparisons between the 
analytical solutions and the numerical approximation, similar as the 
ones made for the linear density case.
Although in the exponential density scenario the problem is more 
complex due to the fact that the density-based discretization must be 
used together with the modified adaptive discretization algorithm.
This means that both the distance-size ratio $D$ and the delta ratio 
$\delta$ must be simultaneously determined.
